\cvsection{Experience}
\begin{cventries}
    \cventry
        {Researcher, Lecturer and Teaching assistant}
        {Norwegian University of Life Sciences (NMBU) and NIBIO}
        {Ås, Norway}
        {April 2022 - August 2025}
        {
            \begin{cvitems}
                \item {Literature review published in the Forests journal under the MDPI publishing house.}
                \item {Developed program using object detection models for optical character recognition of codes used to track logs from harvest site to saw mill.}
                \item {Developed program where the object detection model YOLO is compared to semantic segmentation model U-net for the purpose of volume estimation of consignments of logs.} % Developed a pipeline instead of "writing manuscript"
                % \item {Working on project comparing traditional photogrammetry with deep learning based methods (NeRF) for generating 3D representations of lumber to improve accuracy of log scaling.}
                \item {Teaching assistant "DAT300 - Applied Deep Learning"}
                \item {Lecturer and Course manager "IMRT100 - Introductory Course, Subject-oriented Project" and  "DAT200 - Applied Machine Learning"}
                %\item {Subject manager "DAT200 - Applied Machine Learning"}
                %\item {Have been a teaching assistant in the course "DAT300 - Applied Deep Learning" in the fall of 2022 and 2023. Have been responsible for hosting and teaching the courses "IMRT100 - Introductory Course, Subject-oriented Project" and "DAT200 - Applied Machine Learning" in the fall of 2023 and spring of 2024 respectively.}%
            \end{cvitems}
        }
    \cventry
        {Embedded Developer}
        {Data Respons R\&D Services}
        {Høvik, Norway}
        {October 2020 - April 2022}
        {      
          \begin{cvitems}
            \item {Worked as a hardware developer and low-level software developer on two major projects. During my two years there I had less than two weeks where I was not invoicing billable hours on a project.}
            % \item {The biggest project I worked on was as a sub-contractor for a German defence company, Henshold Optronics Gmbh. The company was contracted to develop a control system of a military grade sensor package.}
            \item {I was part of a team that was sub-contracted by a German defence company, where I contributed by reviewing hardware designs, testing partial and complete high-power assemblies, and developed and tested dedicated software solutions in C and C++.}
            %\item {The team consisted of a multi-disciplinary team of mechanical engineers, hardware developers and software developers. I contributed by reviewing hardware designs, testing partial and complete high-power assemblies and developed and tested dedicated software solutions in C and C++.}
            % \item {The second project I was a part of consisted of a smaller team, where we were subcontracted to develop an automotive computer for a company working with autonomous vehicles.}
            \item {I was the lead hardware developer in a project for an autonomous vehicle company, responsible for designing and prototyping the hardware assembly for the autonomous-driving-dedicated computer of an autonomous vehicle.}
          \end{cvitems}
        }
   \cventry
        {Head of Electronics Group}
        {Revolve NTNU (Formula Student)}
        {Trondheim, Norway}
        {April 2017 - September 2018}
        {
          \begin{cvitems}
            \item {Revolve NTNU is NTNUs team in the international student competition Formula Student. In Formula Student, teams from different universities compete with Formula-1-style electric race cars that are designed, assembled and tested in-house.}
            \item {My position at Revolve NTNU was Group Leader of the Electronics group, which was responsible for the entire electronic system of the vehicle.}
            % \item {As the group leader I was responsible for supervising the work of eight embedded developers.}
            \item {I developed part of the vehicle safety system, and as Group Leader I also supervised the work of eight embedded developers.}
            % \item {In the summer of 2018 we attended three competitions in Austria, Germany and Spain where we attained the 7th, 2nd and 4th places respectively.}
          \end{cvitems}
        }
\end{cventries}
