 \cventry
        {Embedded Developer - Data Respons R\&D Services}
        {Hensholdt Optronics Gmbh}
        {Oslo, Norway}
        {October 2020 - April 2022}
        {      
          \begin{cvitems}
            \item {The purpose of the project was to design, and produce a prototype of a control system for a sensor package consisting of multiple cameras and laser pointers.}
            \item {The team consisted of mechanical, hardware and software engineers. I was originally brought aboard as a hardware developer, but I moved over to software development after the hardware design was complete.}
            \item {Assisted with review of hardware components, and schematics.}
            \item {Did bring-up testing of multiple PCB assemblies, and performed high power tests on the complete assembly.}
            \item {Programmed drivers for ADS1015, and ADS112 ADCs in C.}
            \item {Performed code-review for safety critical software written in C++, and set up a linter, and a static code analysis tools to ensure the software followed the rules required.}
          \end{cvitems}
        }
    \cventry
        {Embedded Developer - Data Respons R\&D Services}
        {Autonomous vehicle company}
        {Oslo, Norway}
        {June 2021 - December 2021}
        {      
          \begin{cvitems}
            \item {The company was a customer of Data Respons R\&D Services, but I cannot disclose the company's name.}
            \item {I was the lead hardware designer in a project creating an automotive computer for a company working with autonomous vehicles. The computer consisted of three PCB assemblies.}
            \item {A computing platform was designed with: A SOM for performing image processing tasks, a real-time embedded microcontroller to keep track of multiple communication busses (CAN, RS-232, RS-485 and USB) and an Ethernet switch to allow for communication with multiple Ethernet devices.}
            \item {An I/O shield was made with the purpose of isolating each communication-bus.}
            \item {A power board was made with an automotive-grade surge stopper, a common mode line filter and four different isolated power supplies.}
          \end{cvitems}
        }
        \cventry
        {Summer Intern at System Integration Group}
        {Nordic Semiconductor ASA}
        {Oslo, Norway}
        {June 2019 - August 2019}
        {      
          \begin{cvitems}
            \item {Took a two week course on digital design with SystemVerilog.}
            \item {The remaining six weeks were spent testing an enterprise tool for verifying timing constraints (false paths and multi-cycle paths) of digital designs.}
          \end{cvitems}
        }
        \cventry
        {Summer intern at Project Local Hawk}
        {Kongsberg Defence and Aerospace AS}
        {Kongsberg, Norway}
        {June 2017 - August 2017}
        {      
          \begin{cvitems}
            \item {Part of a multidisciplinary team of summer interns working on creating an autonomous drone.}
            \item {I was put on the electronics group, and was given various smaller tasks to perform. The tasks were to To configure and test a radio communication link, solder and test a UART-to-RS232 converter and solder and assemble an in-line current sensor, and define a simple coulomb-counting algorithm for estimating state-of-charge of the drones battery.}
          \end{cvitems}
        }
    \cventry
        {Board member and Head of company contacts in 2017}
        {Elektronikk- og Teknologidagen (Electronics and Technology-fair)}
        {Trondheim, Norway}
        {February 2016 - February 2017}
        {
          \begin{cvitems}
            \item {Companies we consider to be potential employers come to campus and have stands, give motivational speeches and conduct job interviews with students. Head of company contacts was responsible for getting companies to participate and was also responsible for 20 other business contacts who also contacted companies.}
          \end{cvitems}
        }
    \cventry
        {Summer Intern at Department of Circulation and Medical Imaging}
        {NTNU, Faculty of Medicine}
        {Trondheim, Norway}
        {August 2020 - October 2020}
        {      
          \begin{cvitems}
            \item {Helped make a simple web-application where clinicians without a programming background could apply the machine learning pipelines developed at the Department on their own datasets.}
          \end{cvitems}
        }
    \cventry
        {Teaching assistant in courses}
        {NTNU, Faculty of Information Technology and Electrical Engineering}
        {Trondheim, Norway}
        {January 2017 - May 2020}
        {      
          \begin{cvitems}
            \item {TFE4172 - Introduction to Semiconductor Devices (Undergraduate course): The job entailed correcting, and supervising students with group projects.}
            \item {TFE4280 - Sensors and Instrumentation (Undergraduate course): The job entailed correcting student-submitted exercises, and helping students with lab-work.}
          \end{cvitems}
        }
        